RNeXML: a package for reading and writing richly annotated phylogenetic, character, and trait data in R

### 2015-01-03 manuscripts/manuscript.Rmd
Fixes and additions to Acknowledgments.

## Acknowledgements
<!-- FIXME Rutger, Hilmar, add whatever you'd like to acknowledge here -->.

This project was supported in part by a grant from the Alfred P Sloan
Foundation Grant 2013-6-22 (CB and SC), NSF Grant DBI-1306697 (CB), ... 
We thank F. Michonneau for helpful comments on an earlier version
of this manuscript.
`RNeXML` is part of the rOpenSci project, [http://ropensci.org].

>>>>

## Acknowledgements

This project was supported in part by the National Evolutionary
Synthesis Center (NESCent) (NSF #EF-0905606), and grants from the
Natioal Science Foundation (DBI-1306697) and the Alfred P Sloan
Foundation (Grant 2013-6-22). `RNeXML` started as a project idea for
the Google Summer of Code, and we thank Kseniia Shumelchyk for taking
the first steps to implement it. We are grateful to F. Michonneau for
helpful comments on an earlier version of this manuscript.
